Appendix S1: Supporting Tables and Figures.

### 2022-06-26 ms/SI.Rmd
fix table direction and site information

---
title: "Maenpuen *et al.* --American Journal of Botany-- Appendix S1"
geometry: margin=1in
link-citations: yes
csl: templates/american-journal-of-botany.csl
bibliography: leaf_disc.bib
fontsize: 12pt
#font-famliy: "ebgaramond"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
#  - \usepackage{lineno}
#  - \linenumbers
output:
  html_document:
    fig_caption: yes
    theme: spacelab #readable #sandstone #spacelab #flatly
    highlight: pygments #tango #kate
    toc: TRUE
    toc_depth: 2
    number_sections: FALSE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
      toc: true
  pdf_document:
    keep_md: false
    fig_caption: yes
    keep_tex: yes
    toc: yes
    number_sections: no
    template: templates/eisvogel2.tex
    #template: null
    # pandoc_args:
    #   - "--filter"
    #   - "pandoc-crossref"
  word_document:
    fig_width: 6
    fig_caption: yes
    toc: FALSE
    reference_docx: templates/rmd_style.docx
    pandoc_args:
    - "--filter"
    - "pandoc-crossref"
    - "--mathml"
---

@@

# https://github.com/haozhu233/kableExtra/issues/47
options(kableExtra.auto_format = FALSE)
# for dependency
#targets::tar_load(yml)
#  for non-targets
# val <- yaml::yaml.load_file("../values.yml")
#val <- yaml::yaml.load_file("values.yml")
```

# Appendix S1:

Supporting Tables and Figures.

@@

Site information.
MAT: mean annual temperature,
MAP: mean annual precipitation,
CV: coefficient of variation

```{r, echo=FALSE, caption = "hopge"}
library(jsonlite)
#site <- fromJSON("../data/site_info.json")
#site <- fromJSON("data/site_info.json")
site <- fromJSON(here("data", "site_info.json"))
site |>
  kable(format = "latex",
    caption = "Site information.
              MAT: mean annual temperature,
              MAP: mean annual precipitation,
              CV: coefficient of variation") |>
  # kable_styling() |>
  kable_styling(latex_options = "scale_down") |>
  # column_spec(13:16, width = "2cm") |>
  column_spec(1:16, width = "2cm") |>
  kableExtra::landscape()
```

@@

# Table S2:

@@

```{r, eval=TRUE, echo=FALSE}
dm_glmm <- read_csv(here("data", "dm_glmm.csv"))
dm_glmm |>
  kable(format = "latex") |>
  kable_styling()
```

@@

![](../figs/S2.jpeg)

@@

Figure: Relationships between species mean leaf mass per area (LMA) and leaf tissue density (LD) determined by using whole leaves and leaf discs for the Yunnan dataset that has both leaf thickness for leaf discs and whole leaves.
Dashed lines indicate 1:1 lines.
Blue solid lines indicate standardized major axis regressions.
The 95% confidence intervals are presented as the shaded area.
All the correlations are significant (*P* < 0.001).

>>>>

---
title: "Appendix S1: Supporting Tables and Figures."
#title: "Maenpuen *et al.* --American Journal of Botany-- Appendix S1"
geometry: margin=1in
link-citations: yes
csl: templates/american-journal-of-botany.csl
bibliography: leaf_disc.bib
fontsize: 12pt
#font-famliy: "ebgaramond"
mainfont: Arial
sansfont: Arial
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
  - \usepackage{xcolor}
  - \usepackage{caption}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}  # enable header
  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
  - \fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S1} # add header on right side
 # - \captionsetup[figure]{name=Figure S} #  - \usepackage{lineno}
#  - \linenumbers
output:
  html_document:
    fig_caption: yes
    theme: spacelab #readable #sandstone #spacelab #flatly
    highlight: pygments #tango #kate
    toc: TRUE
    toc_depth: 2
    number_sections: FALSE
    toc_float:
      collapsed: TRUE
      smooth_scroll: TRUE
      toc: true
  bookdown::pdf_document2:
    citation_package: default
    toc: yes
    number_sections: no
    fig_caption: no
    keep_tex: yes
    # template: templates/eisvogel2.tex
---

@@

# https://github.com/haozhu233/kableExtra/issues/47
options(kableExtra.auto_format = FALSE)
```

@@

Site information.
MAT: mean annual temperature,
MAP: mean annual precipitation,
CV: coefficient of variation.

```{r, echo=FALSE, caption = "hopge"}
library(jsonlite)
site <- fromJSON(here("data", "site_info.json"))
site2 <- t(site)
site2[1,] <- t(site)[2,]
site2[2,] <- t(site)[1,]
colnames(site2) <- site2[1,]
site2 <- site2[-1,]
site2 |>
  kbl(booktabs = TRUE, escape = FALSE, format = "latex") |>
  #kable(format = "simple") |>
    # caption = "Site information.
    #           MAT: mean annual temperature,
    #           MAP: mean annual precipitation,
    #           CV: coefficient of variation") |>
  kable_styling(latex_options = c("striped", "HOLD_position")) |>
  column_spec(1:5, width = "3cm")# |>
#  kableExtra::landscape()
```

@@

\newpage
# Table S2:

@@

```{r, eval=TRUE, echo=FALSE}
dm_glmm <- read_csv(here("data", "dm_glmm.csv"))
dm_glmm |>
  rename(`\\textit{P} value` = `*P* value`) |>
  kbl(booktabs = TRUE, escape = FALSE, format = "latex") |>
  kable_styling(latex_options = c("striped", "HOLD_position"))
```

@@

![](../figs/S2.jpeg){ width="470" style="display: block; margin: 0 auto" }

@@

Relationships between species mean leaf mass per area (LMA) and leaf tissue density (LD) determined by using whole leaves and leaf discs for the Yunnan dataset that has both leaf thickness for leaf discs and whole leaves.
Dashed lines indicate 1:1 lines.
Blue solid lines indicate standardized major axis regressions.
The 95% confidence intervals are presented as the shaded area.
All the correlations are significant (*P* < 0.001).

### 2022-06-26 ms/SI.tex
fix table direction and site information

%%
% Copyright (c) 2017 - 2020, Pascal Wagler;
% Copyright (c) 2014 - 2020, John MacFarlane
%
% All rights reserved.
%
% Redistribution and use in source and binary forms, with or without
% modification, are permitted provided that the following conditions
% are met:
%
% - Redistributions of source code must retain the above copyright
% notice, this list of conditions and the following disclaimer.
%
% - Redistributions in binary form must reproduce the above copyright
% notice, this list of conditions and the following disclaimer in the
% documentation and/or other materials provided with the distribution.
%
% - Neither the name of John MacFarlane nor the names of other
% contributors may be used to endorse or promote products derived
% from this software without specific prior written permission.
%
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
% "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
% LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS
% FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE
% COPYRIGHT OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT,
% INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING,
% BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES;
% LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER
% CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
% LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN
% ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE
% POSSIBILITY OF SUCH DAMAGE.
%%

%%
% This is the Eisvogel pandoc LaTeX template.
%
% For usage information and examples visit the official GitHub page:
% https://github.com/Wandmalfarbe/pandoc-latex-template
%%

\DeclareUnicodeCharacter{2212}{-}

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*,table}{xcolor}
%
\documentclass[
  12pt,
  a4paper,
,tablecaptionabove
]{scrartcl}
\usepackage{lmodern}
\usepackage{setspace}
\setstretch{1.2}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\definecolor{default-linkcolor}{HTML}{A50000}
\definecolor{default-filecolor}{HTML}{A50000}
\definecolor{default-citecolor}{HTML}{4077C0}
\definecolor{default-urlcolor}{HTML}{4077C0}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Maenpuen et al. --American Journal of Botany-- Appendix S1},
  hidelinks,
  breaklinks=true,
  pdfcreator={LaTeX via pandoc with the Eisvogel template}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
% add backlinks to footnote references, cf. https://tex.stackexchange.com/questions/302266/make-footnote-clickable-both-ways
\usepackage{footnotebackref}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

% Make use of float-package and set default placement for figures to H.
% The option H means 'PUT IT HERE' (as  opposed to the standard h option which means 'You may put it here if you like').
\usepackage{float}
\floatplacement{figure}{H}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{Maenpuen \emph{et al.} --American Journal of Botany-- Appendix
S1}
\date{}

%%
%% added
%%

%
% language specification
%
% If no language is specified, use English as the default main document language.
%

\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
    % Workaround for bug in Polyglossia that breaks `\familydefault` when `\setmainlanguage` is used.
  % See https://github.com/Wandmalfarbe/pandoc-latex-template/issues/8
  % See https://github.com/reutenauer/polyglossia/issues/186
  % See https://github.com/reutenauer/polyglossia/issues/127
  \renewcommand*\familydefault{\sfdefault}
    % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi

%
% for the background color of the title page
%

%
% break urls
%
\PassOptionsToPackage{hyphens}{url}

%
% When using babel or polyglossia with biblatex, loading csquotes is recommended
% to ensure that quoted texts are typeset according to the rules of your main language.
%
\usepackage{csquotes}

%
% captions
%
%\definecolor{caption-color}{HTML}{777777}
\definecolor{caption-color}{HTML}{37474F}
%\usepackage[font={stretch=1.2}, textfont={color=caption-color}, position=top, skip=4mm, labelfont=bf, singlelinecheck=false, justification=raggedright]{caption}
\usepackage[font={stretch=1}, textfont={color=caption-color}, position=top, skip=2mm, labelfont=bf, singlelinecheck=false, justification=raggedright]{caption}
\setcapindent{0em}

%
% blockquote
%
\definecolor{blockquote-border}{RGB}{221,221,221}
\definecolor{blockquote-text}{RGB}{119,119,119}
\usepackage{mdframed}
\newmdenv[rightline=false,bottomline=false,topline=false,linewidth=3pt,linecolor=blockquote-border,skipabove=\parskip]{customblockquote}
\renewenvironment{quote}{\begin{customblockquote}\list{}{\rightmargin=0em\leftmargin=0em}%
\item\relax\color{blockquote-text}\ignorespaces}{\unskip\unskip\endlist\end{customblockquote}}

%
% Source Sans Pro as the de­fault font fam­ily
% Source Code Pro for monospace text
%
% 'default' option sets the default
% font family to Source Sans Pro, not \sfdefault.
%
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
    \usepackage[default]{sourcesanspro}
  \usepackage{sourcecodepro}
  %\usepackage{}
  \else % if not pdftex
    \usepackage[default]{sourcesanspro}
  \usepackage{sourcecodepro}
  %\usepackage{}

  % XeLaTeX specific adjustments for straight quotes: https://tex.stackexchange.com/a/354887
  % This issue is already fixed (see https://github.com/silkeh/latex-sourcecodepro/pull/5) but the
  % fix is still unreleased.
  % TODO: Remove this workaround when the new version of sourcecodepro is released on CTAN.
  \ifxetex
    \makeatletter
    \defaultfontfeatures[\ttfamily]
      { Numbers   = \sourcecodepro@figurestyle,
        Scale     = \SourceCodePro@scale,
        Extension = .otf }
    \setmonofont
      [ UprightFont    = *-\sourcecodepro@regstyle,
        ItalicFont     = *-\sourcecodepro@regstyle It,
        BoldFont       = *-\sourcecodepro@boldstyle,
        BoldItalicFont = *-\sourcecodepro@boldstyle It ]
      {SourceCodePro}
    \makeatother
  \fi
  \fi

%
% heading color
%
\definecolor{heading-color}{RGB}{40,40,40}
\addtokomafont{section}{\color{heading-color}}
% When using the classes report, scrreprt, book,
% scrbook or memoir, uncomment the following line.
%\addtokomafont{chapter}{\color{heading-color}}

%
% variables for title and author
%
\usepackage{titling}
\title{Maenpuen \emph{et al.} --American Journal of Botany-- Appendix
S1}
\author{}

%
% tables
%

%
% remove paragraph indention
%
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines

%
%
% Listings
%
%

%
% header and footer
%
\usepackage{fancyhdr}

\fancypagestyle{eisvogel-header-footer}{
  \fancyhead{}
  \fancyfoot{}
  \lhead[]{Maenpuen \emph{et al.} --American Journal of Botany--
Appendix S1}
  \chead[]{}
  \rhead[Maenpuen \emph{et al.} --American Journal of Botany-- Appendix
S1]{}
  %\lfoot[\thepage]{}
  \cfoot[]{}
  \cfoot[]{\thepage}
  \renewcommand{\headrulewidth}{0.0pt}
 % \renewcommand{\footrulewidth}{0.0pt}
 % \renewcommand{\headrulewidth}{0.4pt}
 % \renewcommand{\footrulewidth}{0.4pt}
}
\pagestyle{eisvogel-header-footer}

%%
%% end added
%%

\begin{document}

%%
%% begin titlepage
%%

%%
%% end titlepage
%%

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\hypertarget{appendix-s1}{%
\section{Appendix S1:}\label{appendix-s1}}

Supporting Tables and Figures.

@@

Site information. MAT: mean annual temperature, MAP: mean annual
precipitation, CV: coefficient of variation

\begin{landscape}\begin{table}

\caption{\label{tab:unnamed-chunk-1}Site information.
              MAT: mean annual temperature,
              MAP: mean annual precipitation,
              CV: coefficient of variation}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}|>{\raggedleft\arraybackslash}p{2cm}}
\hline
Data name & Site name & Vegetation & Elevation (m) & Location & MAT (℃) & MAP (mm) & Dry period (month) & Canopy height (m) & Leaf thickness & Leaf disc thickness & Leaf punch diameter (cm) & Number of species for species means & Number of individuals for individuals means & Number of species for CV & Number of individuals for CV\\
\hline
Yunnan & Bubeng & Tropical forest (TRF) & 780 & 21°37'N, 101°35'E & 21 & 1532.0 & 6 & 35-45 & Measured & Measured & 0.6 & 60 & 366 & 60 & 366\\
\hline
Yunnan & Ailao-shan & Subtropical evergreen wet forest (STF) & 2500 & 24°32'N, 101°01'E & 11.7 & 1931.0 & - & 25 & Measured & Measured & 0.6 & 47 & 282 & 47 & 282\\
\hline
Yunnan & Yuanjiang & Hot-dry savanna  (HDS) & 480 & 23°28'N, 102°10'E & 24.7 & 732.8 & 6 & 6-Apr & Measured & Measured & 0.6 & 34 & 204 & 33 & 203\\
\hline
Yakushima & Yakushima & Warm-temperate forest & 14 - 1748 & 30°38'N, 130°62'E & 8.1 - 19.4 & 4477.0 & - & - & Measured & Not-measured & 1.0 & 193 & 607 & 5 & 26\\
\hline
\end{tabular}}
\end{table}
\end{landscape}

@@

\begin{table}
\centering
\begin{tabular}{r|r|r|r|l}
\hline
Estimate & SE & DF & t-value & *P* value\\
\hline
-4.410 & 0.013 & 1030 & -333.00 & < 0.001\\
\hline
0.240 & 0.007 & 1030 & 33.20 & < 0.001\\
\hline
-0.061 & 0.009 & 1030 & -6.94 & < 0.001\\
\hline
0.277 & 0.008 & 1030 & 34.90 & < 0.001\\
\hline
-0.500 & 0.020 & 332 & -25.60 & < 0.001\\
\hline
\end{tabular}
\end{table}

@@

\includegraphics{../figs/S2.jpeg}

@@

Figure: Relationships between species mean leaf mass per area (LMA) and
leaf tissue density (LD) determined by using whole leaves and leaf discs
for the Yunnan dataset that has both leaf thickness for leaf discs and
whole leaves. Dashed lines indicate 1:1 lines. Blue solid lines indicate
standardized major axis regressions. The 95\% confidence intervals are
presented as the shaded area. All the correlations are significant
(\emph{P} \textless{} 0.001).

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Arial}
  \setsansfont[]{Arial}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Appendix S1: Supporting Tables and Figures.},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancypagestyle{plain}{\pagestyle{fancy}}
\fancyhead[RE,RO]{Maenpuen \textit{et al}. --American Journal of Botany-- Appendix S1}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Appendix S1: Supporting Tables and Figures.}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\newpage

@@

Site information.
MAT: mean annual temperature,
MAP: mean annual precipitation,
CV: coefficient of variation.

\begin{table}[H]
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}>{\raggedright\arraybackslash}p{3cm}}
\toprule
  & Bubeng & Ailao-shan & Yuanjiang & Yakushima\\
\midrule
\cellcolor{gray!6}{Site name} & \cellcolor{gray!6}{Yunnan} & \cellcolor{gray!6}{Yunnan} & \cellcolor{gray!6}{Yunnan} & \cellcolor{gray!6}{Yakushima}\\
Vegetation & Tropical forest (TRF) & Subtropical evergreen wet forest (STF) & Hot-dry savanna  (HDS) & Warm-temperate forest\\
\cellcolor{gray!6}{Elevation (m)} & \cellcolor{gray!6}{780} & \cellcolor{gray!6}{2500} & \cellcolor{gray!6}{480} & \cellcolor{gray!6}{14 - 1748}\\
Location & 21°37'N, 101°35'E & 24°32'N, 101°01'E & 23°28'N, 102°10'E & 30°38'N, 130°62'E\\
\cellcolor{gray!6}{MAT (℃)} & \cellcolor{gray!6}{21} & \cellcolor{gray!6}{11.7} & \cellcolor{gray!6}{24.7} & \cellcolor{gray!6}{8.1 - 19.4}\\
\addlinespace
MAP (mm) & 1532.0 & 1931.0 & 732.8 & 4477.0\\
\cellcolor{gray!6}{Dry period (month)} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{-} & \cellcolor{gray!6}{6} & \cellcolor{gray!6}{-}\\
Canopy height (m) & 35-45 & 25 & 4-6 & -\\
\cellcolor{gray!6}{Leaf thickness} & \cellcolor{gray!6}{Measured} & \cellcolor{gray!6}{Measured} & \cellcolor{gray!6}{Measured} & \cellcolor{gray!6}{Measured}\\
Leaf disc thickness & Measured & Measured & Measured & Not-measured\\
\addlinespace
\cellcolor{gray!6}{Leaf punch diameter (cm)} & \cellcolor{gray!6}{0.6} & \cellcolor{gray!6}{0.6} & \cellcolor{gray!6}{0.6} & \cellcolor{gray!6}{1.0}\\
Number of species for species means & 60 & 47 & 34 & 193\\
\cellcolor{gray!6}{Number of individuals for individuals means} & \cellcolor{gray!6}{366} & \cellcolor{gray!6}{282} & \cellcolor{gray!6}{204} & \cellcolor{gray!6}{607}\\
Number of species for CV & 60 & 47 & 33 & 5\\
\cellcolor{gray!6}{Number of individuals for CV} & \cellcolor{gray!6}{366} & \cellcolor{gray!6}{282} & \cellcolor{gray!6}{203} & \cellcolor{gray!6}{26}\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}[t]{rrrrl}
\toprule
Estimate & SE & DF & t-value & \textit{P} value\\
\midrule
\cellcolor{gray!6}{-4.410} & \cellcolor{gray!6}{0.013} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-333.00} & \cellcolor{gray!6}{< 0.001}\\
0.240 & 0.007 & 1030 & 33.20 & < 0.001\\
\cellcolor{gray!6}{-0.061} & \cellcolor{gray!6}{0.009} & \cellcolor{gray!6}{1030} & \cellcolor{gray!6}{-6.94} & \cellcolor{gray!6}{< 0.001}\\
0.277 & 0.008 & 1030 & 34.90 & < 0.001\\
\cellcolor{gray!6}{-0.500} & \cellcolor{gray!6}{0.020} & \cellcolor{gray!6}{332} & \cellcolor{gray!6}{-25.60} & \cellcolor{gray!6}{< 0.001}\\
\bottomrule
\end{tabular}
\end{table}

@@

\includegraphics[width=4.89583in,height=\textheight]{../figs/S2.jpeg}

@@

Relationships between species mean leaf mass per area (LMA) and leaf tissue density (LD) determined by using whole leaves and leaf discs for the Yunnan dataset that has both leaf thickness for leaf discs and whole leaves.
Dashed lines indicate 1:1 lines.
Blue solid lines indicate standardized major axis regressions.
The 95\% confidence intervals are presented as the shaded area.
All the correlations are significant (\emph{P} \textless{} 0.001).
